An Algebraic Representation of Wireless Workload

### 2008-02-08 paper.tex
Updated plots; finished discussion.

What would better traffic models look like? How can we create them? One possible approach is to use actual traffic traces as we have done. This approach is unsatisfactory, however, because it provides the experimenter with almost no control over experiments. Synthetic models have parameters, which can be tweaked as necessary---adjusting, for example, the number of active nodes in a simulation, without affecting other parameters. Traffic traces, on the other hand, must be used without significant alteration if they are to actually provide the desired realism.

On the other hand, we have discredited both uniform and marginal modeling as viable approaches that can fully address the workload modeling requirements of the wireless research community. This, we believe, is where the General Matrix Model plays a vital role in the development of better models.

>>>>

What would better traffic models look like? How can we create them? One possible approach is to use actual traffic traces as we have done. This approach is unsatisfactory, however, because it provides the experimenter with almost no control over experiments. Synthetic models have parameters, which can be tweaked as necessary---adjusting, for example, the number of active nodes in a simulation, without affecting other parameters. Traffic traces, on the other hand, must be used without significant alteration if they are to actually provide the desired realism. This inability to control all but one or two parameters is nearly crippling for experimental purposes. Therefore, the research community needs models whose parameters can be adjusted independently, but whose performance characteristics can be made to resemble whatever example of network behavior one might need. The General Matrix Model does not yet fulfill this role since its parameters cannot be freely varied. We believe, however, that \caps{GMM} plays a vital role in the ongoing process of developing  of better models. By reducing the general problem of traffic modeling to the domain of linear algebra, we have provided traffic researchers with a vast array of powerful theoretical and computational tools that can be immediately applied to the problem at hand.\footnote{The derived models used in this paper were all implemented in Matlab, each in only a few simple lines. All the models used here are implemented in only 19 lines of code. Of course, the framework to apply them to traffic traces and simulations is significantly larger.} What are the next steps? The authors are currently investigating a variety of matrix factorization and clustering techniques to extract hidden structure from a large and diverse body of real traffic.

%The reader will note that the transformations applied in this paper are all quite simple. Our regularization matrices primarily consisted of ones and zeros. The algebraic representation of complete workload
